Evaluation of the repository

### 2024-11-06 pages/background.qmd
docs(general): minor bits / tidying / removing resolved TODO

@@

@@

* Open license
* Dependency management
* FOSS model
* Minimum documentation
* Open Researcher and Contributor IDs (ORCID)
* Citation information
* Remote code repository
* Open science archive

>>>>

<!--TODO: Write this up, currently just some notes and ideas - or, could leave as notes.-->

@@

(I.e. terminology I researched previously, **computational reproducibiltiy** etc, similar to how lots of articles define it, e.g. @samuel_computational_2024).

@@

* Open licence
* Dependency management
* FOSS model
* Minimum documentation
* Open Researcher and Contributor IDs (ORCID)
* Citation information
* Remote code repository
* Open science archive

### 2024-11-06 pages/reflections.qmd
docs(general): minor bits / tidying / removing resolved TODO

<!-- TODO: Consider whether to make further attempts at managing to backdate R. Didn't manage before. E.g. `containerit` package. Although - is it necessary, if I succeeded without? Note, I always backdated the python environments. So, relatedly, TODO: Is it worth checking/trying with newest Python and seeing if they would work?</mark -->

<!-- TODO: Add reflections related specifically to the reproduction package and second reproduction test parts of the work (i.e. after the reproduction) -->

<!-- TODO: From Tom - So much great work and interesting findings. We need to move towards some headlines and take aways for the community. Mayybe there are some high level groupings of your findings? e.g.

* Study reporting
* Model structuring and functionality
* Analysis pipeline

Or perhaps:

* Evidence supporting the use of reporting guidelines
    * as in - reporting guidelines state this should info be included and you found it v.difficult or impossible to reproduce without it.?
-->

@@

* Models will sometimes work with the latest versions of packages, but likewise, you will sometimes need to backdate as it no longer works with the latest
* For Python, it was very easy to "backdate" the python and package versions. However, I found this very difficult to in R, and ended up always using the latest versions.
* Versions are sometimes provided elsewhere (e.g. in paper, in other repositories), but would be handy to be in model repository itself.
* Handy to provide specific versions too, particularly when there can be reasonably large changes between minor versions.
* This was a very common issue.
* Tom: For R, we are sort of moving towards a pre-built container for an R reproducible pipeline
    * Response: Though being aware that it is possible to successfully reproduce without backdating - didn't run into issues with it for the R models - though that doesn't mean you wouldn't - but it is a sort of "characteristic" of R, that it is *supposed* to be less changeable than Python in this regard. Though obviously no guarantees. And not a fair comparison, as I didn't try to run the Python ones without backdating.

>>>>

@@

* Models will sometimes work with the latest versions of packages, but likewise, you will sometimes need to backdate as it no longer works with the latest
* For Python, it was very easy to "backdate" the python and package versions. However, I found this very difficult to in R, and ended up always using the latest versions.
* Versions are sometimes provided elsewhere (e.g. in paper, in other repositories), but would be handy to be in model repository itself.
* Handy to provide specific versions too, particularly when there can be reasonably large changes between minor versions.
* This was a very common issue.
* Tom: For R, we are sort of moving towards a pre-built container for an R reproducible pipeline
    * Response: Though being aware that it is possible to successfully reproduce without backdating - didn't run into issues with it for the R models - though that doesn't mean you wouldn't - but it is a sort of "characteristic" of R, that it is *supposed* to be less changeable than Python in this regard. Though obviously no guarantees. And **not a fair comparison, as I didn't try to run the Python ones without backdating**.

### 2024-11-06 pages/repo_evaluation.qmd
docs(general): minor bits / tidying / removing resolved TODO

<!-- TODO: Add Johnson et al. 2021 -->

@@

<!-- TODO: Update after Johnson et al. 2021 -->

@@

These topics were covered in the badge criteria reflections: **open licence**, **minimum documentation**, and **open science archive**. <!--TODO: Consider re minimum documentation: Kim met for STARS but not for badges. Double-check that decision-->

@@

**ORCID** and **citation information**: Doesn't impact reproduction in this case - but we do go to these from having found an article. In all cases, I emailed the authors, which requires finding contact information (generally via paper, sometimes from googling them to find new emails).

>>>>

@@

@@

These topics were covered in the badge criteria reflections: **open licence**, **minimum documentation**, and **open science archive**.

@@

**ORCID** and **citation information**: Doesn't impact reproduction in this case - but:

* We do go to these from having found an article. I was choosing repositories that I had found from papers, so I already at least knew who the paper authors were.
* In all cases, I emailed the authors, which requires finding contact information (generally via paper, sometimes from googling them to find new emails).
* Any attempted citation of the repository itself would've necessarily been correct, depending on whether the author list would be the same as in the paper, if you relied on the paper without citation information.
